---
toc: False
fontsize: 16pt
page-layout: full
---
<style>
.navbar-toggler-icon::before {
  font-family: FontAwesome;
  content: "\f0c9"; /* fa-bars, fa-navicon */
}

<style>
  table {
    table-layout: fixed;
  }
  @media all and (max-width:768px) {
        .calculator tr {    display: table;  width:100%;    }
        .calculator td {    display: table-row; }
    }
</style>

</style>

<h1>STAT 1110: Applied Statistical Concepts and Methods</h1>
<h3>Fall 2026 -- Sections S17, S18, and S19</h3>

\

<p>Welcome to the companion course site for STAT 1110, with Dr. Ethan P. Marzban! 


::: {.callout-important}
## **Important**

Please note that this page contains only lecture- and homework-related material. You should consult your section's specific Canvas Page for all remaining material (e.g. Reading Responses, Quiz Solutions, etc.)
:::

```{=html}
<head>
<link href="//maxcdn.bootstrapcdn.com/bootstrap/4.1.1/css/bootstrap.min.css" rel="stylesheet" id="bootstrap-css">
<script src="//maxcdn.bootstrapcdn.com/bootstrap/4.1.1/js/bootstrap.min.js"></script>
<script src="//cdnjs.cloudflare.com/ajax/libs/jquery/3.2.1/jquery.min.js"></script>
<!------ Include the above in your HEAD tag ---------->
</head>

<div class="container mt-5 mb-5">
	<div class="row">
		<div class="col-md-10 offset-md-0">
			<h4>General Weekly Timeline</h4>
			<ul class="timeline">
				<li>
					<a style="color:blue">Homework Released</a>
					<a style="color:blue" class="float-right">M Morning</a>
				</li>
				<li>
					<a style="color:blue">Lecture Slides Released</a>
					<a style="color:blue" class="float-right">M Morning</a>
				</li>
				<li>
					<a style="color:blue">Lecture Activities Released</a>
					<a style="color:blue" class="float-right">MW Morning</a>
				</li>
				<li>
					<a style="color:blue">Lecture Activity Solutions</a>
					<a style="color:blue" class="float-right">MW Evening </a>
				</li>
				<li>
					<a style="color:blue">Homework Solutions</a>
					<a style="color:blue" class="float-right">Th Morning</a>
				</li>
			</ul>
		</div>
	</div>
</div>
```


```{r setup, include = F}
library(googlesheets4)
library(gt)
library(tidyverse)

gs4_deauth()

google_sheet <- read_sheet("https://docs.google.com/spreadsheets/d/1UQZ_exqPfs3WWzko8dQaYHkqjNLmHmPKxVIPZV5LXaE/edit?usp=sharing")
```

```{r}
#| echo: False

google_sheet %>%
  select(-Admin_Notes, -Day) %>%
  mutate(Date = as.Date(Date)) %>%
  gt() %>%
  fmt_date(Date, date_style = 31) %>%
  sub_missing(columns = c(Week, Reading, Topic, Homework), missing_text = "") %>%
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "#D3D3D3",
      style = "solid"
    ),
    locations = cells_body(
      columns = c(Date, Topic, Reading)
    )
  ) %>%
  cols_align(
    align = "center", 
    columns = c(Week)
  ) %>%
  cols_align(
    align = "right", 
    columns = c(Date)
  ) %>%
  cols_align(
    align = "left", 
    columns = c(`Lecture Slides`,
                `Lecture Activities`
                )
  ) %>%
  fmt_markdown(
    columns = c(Week, Reading, Topic, `Lecture Slides`, `Lecture Activities`, Homework)
  ) %>%
  cols_width(
    Week ~ pct(4),
    Date ~ pct(13), 
    Reading ~ pct(14),
    Topic ~ pct(15),
    `Lecture Slides` ~ pct(18),
    `Lecture Activities` ~ pct(20),
    Homework ~ pct(17)
  ) %>%
  cols_label_with(fn = function(x) {
      janitor::make_clean_names(x, case = "title") %>%
        toupper() %>%
        stringr::str_replace_all("^|$", "**") %>%
        md()
    }) %>%
  tab_options(
    table.font.size = 16) %>%
  opt_row_striping()
```